Interactive Graphics for Visually Diagnosing Forest Classifiers in R

### 2022-10-18 COST_submission_9_Oct22/PPforestViz_journal.tex
update

\institute{Corresponding author: Natalia da Silva \at
              Instituto de Estadística (IESTA), Universidad de la República, Montevideo, Uruguay.\\
              \email{natalia.dasilva@fcea.edu.uy}\\
              ORCID:0000-0002-6031-7451\\
           \and
          Dianne Cook \at 
          Department of Econometrics and Business Statistics, Monash University, Melbourne, Australia.\\
          \email{dicook@monash.edu}\\
          ORCID:0000-0002-3813-7155\\
          \and
          Eun-Kyung Lee \at
          Department of Statistics, Ewha Womans University, Seoul, South Korea.\\
          \email{lee.eunk@gmail.com}
}

>>>>

\institute{Natalia da Silva \at
              Instituto de Estadística (IESTA), Universidad de la República\\
              \email{natalia.dasilva@fcea.edu.uy}
           \and
          Dianne Cook \at 
          Department of Econometrics and Business Statistics, Monash University\\
          \email{dicook@monash.edu}\and
          Eun-Kyung Lee \at
          Department of Statistics, Ewha Womans University\\
          \email{lee.eunk@gmail.com}
}
